How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-17 tse-paper/content.tex
Add new intro

Continuous Integration (CI) has become a common practice in software
engineering~\cite{hilton2016usage}.
Many software projects use
CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect
bugs early~\cite{vasilescu2015quality,duvall2007continuous}, improve
developer productivity~\cite{miller2008hundred,hilton2016usage} and
communication~\cite{downs2012ambient}.
CI builds produce logs which
report results of various sub-steps within the build.
These build logs
contain a lot of valuable information for developers and researchers---for
example, descriptions of compile errors, linter warnings or failed
tests~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.

CI builds produce logs which report the results of the steps within
the build.
The information stored in build logs can and has
already been used for a variety of applications.
One prominent dataset
in the space, TravisTorrent, was featured as the MSR Data Challenge
2017~\cite{msr17challenge}.
To date, scientist and practitioners alike
have used it and other, proprietary datasets to understand and
cateogrize Continuous Integration build
failures~\cite{islam2017insights}, to do research on testing
practices~\cite{orellana2017differences}, to train classifiers to
predict the build outcome and
duration~\cite{ni2017cost,bisong2017built,machalica2019predictive},
and to investigate static analysis tools in CI
builds~\cite{zampetti2017open}.
Therefore, being able to efficiently
and correctly extract information from build logs is paramount to the
future of a variety of fields depending on it.

However, build logs can be verbose and large---sometimes in excess of
50 MB of ASCII text~\cite{beller2017oops}---making them inadequate
for direct human consumption.
Therefore, to support developers and
researchers in efficiently making use of the information within build
logs, we must at least semi-automatically retrieve the chunks of the
log that describe the targeted information.

There are different techniques to retrieve information chunks from CI
build logs.
Beller et al.\ use a rule-based system of regular
expressions to analyze logs from Travis CI~\cite{beller2017oops}.
Such regular expressions are developed by looking at exemplary build
logs.
Vassallo et al.\ wrote a custom parser to gather information
for build repair hints~\cite{vassallo2018un-break}.
Recently, Amar et
al.\ reduced the number of lines for a developer to inspect by
creating a diff between logs from failed and successful
builds~\cite{amar2019mining}.

These approaches have various strengths and weaknesses: Regular
expressions are exact, but tedious and error-prone to
maintain~\cite{michael2019regexes}.
Custom parsers are powerful
though fragile in light of changes in the log structure.
Diffing
between failed and successful logs can reduce the information to be
processed, but is at best semi-automatic~\cite{amar2019mining}.

% TODO: 4 sentence description of the steps in graphic?
\Cref{fig:overview} gives an overview of our research steps.
We conducted a systematic mapping study,
to gain an impression on how researchers are using information from
build logs within their research or to support
developers.
% We implemented three promising techniques that retrieve
% chunks of text from build logs and can be adapted to
% a specific project and use case by giving examples of build logs and
% correpsonding chunks.
% We evaluated the
Our goal was to clarify the state-of-research on build log
analysis (\textbf{RQ1}).

The outcomes of our study shows that there are various attempts to
retrieve specific information from buildlogs.
The resulting implementations are rarely available and therefore rarely
reused.
Because of the high development overhead
of the custom parsers, many implementations are limited to small number
of supported build tools.

\begin{figure*}[htb]
	\centering
	\includegraphics[width=\textwidth, trim={1.2cm 10.5cm 1.2cm 0cm},
	clip]{img/overview.pdf}
	\caption{Our Research Workflow.}
	\label{fig:overview}
\end{figure*}

To address this, we implement three promising techniques for build
log analysis.
They retrieve specific chunks of targeted information and are trained
with examples provided by the user.
We conduct an empirical study on the \emph{LogChunks} data
set~\cite{brandt2020logchunks} to
gauge the performance of these chunk retrieval techniques and characterize
when one of the techniques should be preferred over other alternatives
(\textbf{RQ2}).

\begin{simplebox}[minipage boxed title*=-5cm]{Research Questions}
\begin{itemize}
  \item[\textbf{RQ1:}] What is the state-of-research on build
  log analysis?
  \item[\textbf{RQ2:}] When are PBE, CTS or KWS suited to
  retrieve chunks from build logs?
\end{itemize}
\end{simplebox}

% also moved down to where mentioned in detail
% left copy here for convenience

% \begin{simplebox}[attach boxed title to top center={yshift=-6mm}]
% {\textbf{RQ1:} What is the state-of-research on build
% log analysis?}
% \begin{itemize}
%   \item[\textbf{RQ1.1:}] Which information is targeted?
%   \item[\textbf{RQ1.2:}] Which techniques are used?
%   \item[\textbf{RQ1.3:}] Which build logs are analyzed?
% \end{itemize}
% \end{simplebox}

% \begin{simplebox}[minipage boxed title*=-2.5cm,
% attach boxed title to top center={yshift=-6mm}]
% {\textbf{RQ2:} When are PBE{,} CTS or KWS suited to
% retrieve chunks from build logs?}
% \begin{itemize}
%   \item[\textbf{RQ2.1:}] How many examples does a technique need to
%   perform best?
%   \item[\textbf{RQ2.2:}] How structurally similar do the examples
%   need for a technique to be applicable?
%   \item[\textbf{RQ2.3:}] How accurate are the retrievals of a technique?
% \end{itemize}
% \end{simplebox}

% % At the moment there is only anecdotal evidence on the performance
% of these
% % techniques and on when a technique should be preferred over other
% alternatives.
% % Developers and researches currently have little support when choosing
% which
% % technique to use for a task.

% % The goal of this article is to investigate different chunk retrieval
% techniques
% % for build logs and describe under which circumstances certain
% techniques
% can be
% % recommended over others.
% % We aim to characterize different chunk retrieval techniques.
% % For \textbf{Research Question 1} (\textbf{RQ1}), we analyze which
% criteria
% % influence the suitability of a chunk retrieval technique for CI
% build logs.

We implement and evaluate three chunk retrieval techniques:
\begin{itemize}
  \item \textbf{Program Synthesis by Example (referred to as PBE)}
  Based on user examples of build logs and chunks, PBE
  synthesizes
  a regular expression matching the given chunks within the build logs.
  \item \textbf{Common Text Similarity (CTS)}
  Using the Vector Space Model, CTS selects those lines of a log which are
  most similar to the lines present in example chunks provided by
  the user.
  \item \textbf{Keyword Search (KWS)}
  Ad-hoc method for finding fitting passages by searching the whole
  text for
  the occurrence of specific trigger words.
\end{itemize}

Following the results from our comparison study,
recommend PBE for use cases where the desired information is always
represented in the same structural way and high confidence in precision
and recall of the chunk retrieval is required.
Results produced by PBE are suited for automatic on-ward processing.
CTS is well suited when the representation of the desired information
varies
slightly and the output of the chunk retrieval is further processed by
a human.
In cases where the textual representation of the desired information in
the log
is unpredictable or varies greatly, KWS seems to be the best choice.
However,
its low precision---it extracts a context of multiple lines around a
finding---makes it generally unsuited for automatic on-ward processing and
instead requires a human to further inspect and interpret the output
chunk.

@@

% TODO: this could move to the chunk retrieval techniques section
The results of our empirical comparison study on the chunk retrieval
techniques
show that the structural representation of the targeted chunk greatly
influences
the performance of the chunk retrieval techinques.
\Cref{lst:chunk-example} shows two exemplary
log chunks from Android build logs marked in blue.
Both chunks contain the information on why the
corresponding build failed.
When PBE is trained with these two examples it produces
a regular expression program similar to the one presented in
\Cref{lst:prose-program-simplified}.
The retrieval
starts after a colon and a line separator and before a capital
letter.
It ends before two line separators, consistent with the two example
chunks from \Cref{lst:chunk-example}.
This shows, that the characters structuring the text around the chunk are
cruicial for regular expressions to identify a log chunk.
In fact, if the third example from \Cref{lst:chunk-example-3} with a
different structural representation is added to the training set,
PBE is not able to syntesize a program and returns
``\texttt{no program found}''.
We express this difference in structural representation through
dividing log chunks into structural categories.
The chunks from \Cref{lst:chunk-example}
are in the \emph{same structural category}, while the chunk from
\Cref{lst:chunk-example-3} is in a \emph{different structural category}.

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\columnwidth, clip]{img/lit_survey.pdf}
	\caption{Our literature selection process, following
	\cite{petersen2015guidelines}.}
	\label{fig:lit-survey}
\end{figure}

@@

In summary, this literature study shows the need for build log
analysis techniques that are build-environment agnostic, automated
and can be configured by the user with little effort.
We achieve this by developing three techniques for which the
information to be retrieved is specified through examples or keywords.

@@

\subsection{Characteristics of Chunk Retrieval Techniques}
\label{sec:crt-characteristics}
In this article, we evaluate different techniques to automatically
retrieve pieces of information that appear literally in the build
logs.
%, i.e., techniques that do not aggregate, combine, or deducted
%information.
We call such pieces of information from build logs
\emph{chunks}, and the techniques \emph{chunk retrieval techniques}.
The techniques we investigate here do not require a formal lexer and
parser to analyze the entire structure of build logs, but focus on
ad-hoc extracting just one specific piece of information per
configuration.

@@

To investigate when our chunk retrieval techniques are suited to
analyze build logs (\textbf{RQ2}), we perform an empirical comparison
study on the \emph{LogChunks} data set~\cite{brandt2020logchunks}.
In particular we are interested in how many examples a technique
should be trained with for best performance (\textbf{RQ2.1}),
how similar the structural representation of the targeted log chunks
has to be (\textbf{RQ2.2}) and how reliable the quality of the
produced outputs are (\textbf{RQ2.3}).

@@

In the following we present the data set we created for this study,
our study process (presented in \Cref{fig:study}) and the metrics
we measure to answer our research questions.

\begin{figure*}[tb]
	\centering
	\includegraphics[width=\textwidth, trim={1.6cm 1.6cm 0.2cm 5.6cm},
  clip]{img/study.pdf}
	\caption{Design of our technique comparison study.}
	\label{fig:study}
\end{figure*}

\subsection{LogChunks}
For this study we created the previously published data set
\emph{LogChunks}.
It encompasses 797 build logs from Travis CI,
stemming from a broad range of 80 GitHub repositories and 29
programming languages.
For each file, the authors manually ``labeled
the log part (chunk) describing why the build
failed''~\cite{brandt2020logchunks}.
We included keywords, which we
would use to search for the selected chunk within the log.
In
addition, we categorized the log chunks according to their format
within the log.
If the chunks were surrounded by the same markings
within the log we assigned them the same structural category.

\subsection{Study Process}
We begin by selecting all examples in \emph{LogChunks}
that correspond to one GitHub repository---end therefore the
same build environment (1).
One to five examples make up the training set (2).
We vary its size to measure how many examples are needed to
confidently configure a technique.
The training set is so small, because the examples have to be
manually created by a user.
A larger training set would oppose our goal of providing techniques
that can be configured with little effort.
The example chronologically after the training set makes up the
test set (3).
In this way, we train on examples from past build logs and test on
more recent logs.
We chose a training set size of 1, as users of our techniques
should receive reliable results on every build log they analyze.
As a next step, we configure the chunk retrieval technique with
the examples from the training set (4) and apply the technique to the
training set (5), which produces the retrieval output (6).
Based on this, we collect the following measurements (7):
\begin{itemize}
  \item The size of training set (\textbf{RQ2.1}),
  \item the number of structural categories in the training set
  (\textbf{RQ2.2})
  \item the lines of the retrieval output ($\mathit{RetrievedLines}$),
  and our oracle, the output defined in the test example
  ($\mathit{DesiredLines}$).
  From these we calculate accuracy metrics (\textbf{RQ2.1}).
\end{itemize}

\textbf{Accuracy Metrics}
We calculate a number of accuracy metrics to measure how well
the chunk retrieval techniques perform in our evaluation:

@@

	% What about when a line is replicated twice?
	% I.e., Are line numbers part of this? => no.
	% not checked, but if lines are identical they also contain
	% the same information so if someone asks we can defend I think

	\item $\mbox{Precision} = \dfrac{|\mathit{True\
	Positives}|}{|\mathit{RetrievedLines}|}$ \vspace{0.21cm} \\
	Precision of a chunk retrieval describes which proportion of
	the retrieved lines were actually desired.

	\item $\mbox{Recall} =
	\dfrac{|\mathit{True\ Positives}|}{|\mathit{DesiredLines}|}$
	\vspace{0.2cm} \\
	Recall of a chunk retrieval describes which proportion of the
	desired lines were retrieved.

	\item $\mbox{F$_{1}$-score} = 2 \cdot \dfrac{\mathit{Precision}
	\cdot \mathit{Recall}}{\mathit{Precision} + \mathit{Recall}}$
	\vspace{0.2cm}\\
	In addition, we calculate the F$_{1}$-score, the harmonic mean
	of precision and recall.
  We prefer F$_{1}$ to other aggregate
	measures such as accuracy because for a
	``needle-in-the-haystack'' scenario, we want to avoid bloating
	our results by correctly not finding lots of irrelevant log
	lines.

	\item Successful retrieval = $\mathit{true}\ \mathit{iff}\
	\mathit{Recall} = 1, \mathit{false\ otherwise}$ \vspace{0.05cm}\\
	We define a successful retrieval as one where all desired
	lines were
	extracted, therefore when recall is one.
\end{itemize}

This concludes one execution within our evaluation.
We conduct one run for each of the four chunk retrieval techniques,
for each of the eighty repositories in \emph{LogChunks} (8)
and for each of the five training set sizes (2).
In total we perform 1600 runs, 400 for each of the chunk retrieval
techniques PBE, CTS, KWS and RLR.

Our implementation of the techniques, as well as our evaluation
harness and the code we used to process our results is offered
for inspection and reproduction in our replication package
~\cite{brandt2020chunk-replication}.

>>>>

Within the past two decades, Continuous Integration (CI) has become a
ubiquitous best practice to streamline the build process of software
projects~\cite{hilton2016usage,beller2017oops,staahl2014modeling}. Build
logs are a textual by-product that automatic software build processes
create. As a ``treasure trove'' of information, they contain results
not only of the elemntary steps to ``make'' a project---such as
retrieving and resolving dependencies, compiling, and testing the
software---but also about anciliary quality assurance steps such as
automated, static analysis tools.

When a build or one of its sub steps fails, developers typically
scavenge the log for the source of the error. This manual activity is
tedious and prone to error~\cite{santolucito2018statically}. As a
single build log can be over 50 megabytes large~\cite{beller2017oops},
it finding a piece of information in it is akin to searching for a
needle in a haystack.  In addition, due to their information richness,
build logs enable a plethora of other applications: with the help of
build logs, we can better understand and cateogrize Continuous
Integration failures and compile
errors~\cite{islam2017insights,seo2014programmers}, differentiate
testing practices~\cite{orellana2017differences,vassallo2017a-tale},
train classifiers to predict the build outcome and
duration~\cite{ni2017cost,bisong2017built,machalica2019predictive}, or
investigate static analysis tools in CI
builds~\cite{zampetti2017open}. Manual analysis of build logs does not
scale to the number of build logs and amount of information that such
sophisticated applications require. Therefore, being able to
automatically extract pieces of information from build logs
is not only paramount to such applications, but can also help
developers debug a broken build.

However, despite its paramount role, the process of how to analyze
build logs has so far received little attention, bringing us to our first research question:
\begin{simplebox}[minipage boxed title*=-5cm]{Research Question}
\begin{itemize}
  \item[\textbf{RQ1:}] What are the state-of-the-art techniques on build
  log analysis?
 \end{itemize}
\end{simplebox}

In this article, as first step (\Cref{fig:overview}), we show that
less than half of the 61 works which rely on build log analysis
describe how they performed it, and even fewer did so in detail, let
alone made their implementation available. Even so, the literature
survey finds three main strategies to extract information chunks from
build logs: Using 1) a set of manually curated regular expressions,
similar to TravisTorrentI~\cite{beller2017oops}, 2) a list of keywords
to identify regions of interest in the build log, and 3)
% TODO (Caro): Provide better description
doing text-similarity.

Even though these three approaches to retrieve information chunks from
build logs have different strengths and weaknesses, the literature
survey shows that their use is often arbitrary and that there is
usually no discussion on why to use one over the other. Developers and
researchers not only seem to lack awareness of which techniques exist
(RQ1), but also guidelines on when to employ which. As a consequence,
in RQ2 we ask:

\begin{simplebox}[minipage boxed title*=-5cm]{Research Question}
\begin{itemize}
  \item[\textbf{RQ2:}] What are the comparative strengths and weaknesses of the top-3 build log anaylsis techniques?
\end{itemize}
\end{simplebox}

To answer this question, we implement three automatic techniques for
build log analysis based on the three stratgies at large (step 2):

\begin{itemize}
  \item \textbf{Program Synthesis by Example (referred to as PBE)}
  Based on user examples of build logs and chunks, PBE
  synthesizes
  a regular expression matching the given chunks within the build logs.
  \item \textbf{Common Text Similarity (CTS)}
  Using the Vector Space Model, CTS selects those lines of a log which are
  most similar to the lines present in example chunks provided by
  the user.
  \item \textbf{Keyword Search (KWS)}
  Ad-hoc method for finding fitting passages by searching the whole
  text for
  the occurrence of specific trigger words.
\end{itemize}

In step 3, we conduct an empirical study to gauge the performance of
these chunk retrieval techniques under a variety of conditions in
real-world projects. Finally, we develop guidelines (step 4) on when
one of the techniques might be perferrential to its alternatives.

\begin{figure*}[htb]
	\centering
	\includegraphics[width=\textwidth, trim={1.2cm 10.5cm 1.2cm 0cm},
	clip]{img/overview.pdf}
	\caption{Research Design.}
	\label{fig:overview}
\end{figure*}

We recommend PBE for use cases where the desired information is always
represented in the same structural way and high confidence in
precision and recall of the chunk retrieval is required.  Results
produced by PBE are suited for automatic on-ward processing.  CTS is
well suited when the representation of the desired information varies
slightly and the output of the chunk retrieval is further processed by
a human.  In cases where the textual representation of the desired
information in the log is unpredictable or varies greatly, KWS seems
to be the best choice.  However, its low precision---it extracts a
context of multiple lines around a finding---makes it generally
unsuited for automatic on-ward processing and instead requires a human
to further inspect and interpret the output chunk.

@@

\subsection{Not intro anymore}
% TODO: this could move to the chunk retrieval techniques section
The results of our empirical comparison study on the chunk retrieval
techniques
show that the structural representation of the targeted chunk greatly
influences
the performance of the chunk retrieval techinques.
\Cref{lst:chunk-example} shows two exemplary
log chunks from Android build logs marked in blue.
Both chunks contain the information on why the
corresponding build failed.
When PBE is trained with these two examples it produces
a regular expression program similar to the one presented in
\Cref{lst:prose-program-simplified}.
The retrieval
starts after a colon and a line separator and before a capital
letter.
It ends before two line separators, consistent with the two example
chunks from \Cref{lst:chunk-example}.
This shows, that the characters structuring the text around the chunk are
cruicial for regular expressions to identify a log chunk.
In fact, if the third example from \Cref{lst:chunk-example-3} with a
different structural representation is added to the training set,
PBE is not able to syntesize a program and returns
``\texttt{no program found}''.
We express this difference in structural representation through
dividing log chunks into structural categories.
The chunks from \Cref{lst:chunk-example}
are in the \emph{same structural category}, while the chunk from
\Cref{lst:chunk-example-3} is in a \emph{different structural category}.

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\columnwidth, clip]{img/lit_survey.pdf}
	\caption{Literature selection process, following
	\cite{petersen2015guidelines}.}
	\label{fig:lit-survey}
\end{figure}

@@

In summary, this literature study shows the need for build log
analysis techniques that are build-environment agnostic, automated
and can be configured with small effort.
We achieve this by developing three techniques for which the
information to be retrieved is specified through examples or keywords.

@@

\subsection{Characteristics of Chunk Retrieval Techniques}
\label{sec:blirt}
In this article, we evaluate different techniques to automatically
retrieve pieces of information that appear literally in the build
logs.
%, i.e., techniques that do not aggregate, combine, or deducted
%information.
We call such pieces of information from build logs
\emph{chunks}, and the techniques \emph{chunk retrieval techniques}.
The techniques we investigate here do not require a formal lexer and
parser to analyze the entire structure of build logs, but focus on
ad-hoc extracting just one specific piece of information per
configuration.

@@

@@

% TODO Caro: redo
\begin{figure*}[tb]
	\centering
	\includegraphics[width=\textwidth, trim={1.6cm 1.6cm 0.2cm 5.6cm},
  clip]{img/study.pdf}
	\caption{Design of our technique comparison study.}
	\label{fig:study}
\end{figure*}

To investigate which technique is best suited to retrieve chunks from
CI build logs we evaluate the three chunk retrieval techniques
PBE, CTS and KWS.
Random Line Retrieval (RLR), acts as a baseline for
the comparison.
The following section
describes our study design and which metrics we measure to answer our
research questions.
In the presentation of the results, we first focus
on each of the three techniques and later compare them against each
other.

\subsection{LogChunks}
For this study we created the previously published data set
\emph{LogChunks}.
It encompasses 797 build logs from Travis CI,
stemming from a broad range of 80 GitHub repositories and 29
programming languages.
For each file, the authors manually ``labeled
the log part (chunk) describing why the build
failed''~\cite{brandt2020logchunks}.
We include keywords, which we
would use to search for the selected chunk within the log.
In
addition, we categorized the log chunks according to their format
within the log.
If the chunks are surrounded by the same markings
within the log we assign them the same structural category.

% We run four techniques on the examples from \emph{LogChunks}.

\noindent
\textbf{Training and Test Set}
% TODO Moritz: You said: Add details how key words were extracted.
% Add example?
% how the keywords were put in logchunks does not fit here, that is
% maybe answered 2 paragraphs above already?
% how KWS uses the keywords is already described in the section
% introducing the technique => I would scrap everything but the first
% sentence directly above here :)

% TODO Moritz: You said: Add more details.
% How was the split in numbers?
% this is described in the following paragraph, should we merge them
% (bc there are also no sub-RQs now) or is it close enough? :)
For each repository in \emph{LogChunks}, we split the examples
chronologically into training and test set.
Therefore, we train on
examples from past build logs and test on more recent build logs.

\noindent % TODO: adapt if we change the research questions
\textbf{RQ 2.1: Size of Training and Test Set}
We evaluate the techniques with different training set
sizes, to analyze how many examples the chunk retrieval techniques need to
perform best.
We train each technique with one to five examples from each of
the repositories within \emph{LogChunks}.
The size of the test set is one.

\noindent
\textbf{RQ 2.2: Recording Structural Categories}
We record the structural categories
of the examples in the training and test sets, to determine how
structurally similar the examples for the chunk
retrieval techniques need to be.

\noindent
\textbf{RQ2.3: Accuracy Metrics}
we save the output lines of the chunk retrieval run on the input
of the test example ($\mathit{RetrievedLines}$), to measure the
accuracy of the retrieved chunks
As oracle in our evaluation, we save the
desired lines from the output of the test example
($\mathit{DesiredLines}$).

We calculate and define a number of metrics for the context of our
evaluation.

@@

	% What about when a line is replicated twice?
	% I.e., Are line numbers part of this? => no.
	% not checked, but if lines are identical they also contain
	% the same information so if someone asks we can defend I think
	\item $\mbox{Precision} = \dfrac{|\mathit{True\
	Positives}|}{|\mathit{RetrievedLines}|}$ \vspace{0.21cm} \\
	Precision of a chunk retrieval describes which proportion of
	the retrieved lines were actually desired.

	\item $\mbox{Recall} =
	\dfrac{|\mathit{True\ Positives}|}{|\mathit{DesiredLines}|}$
	\vspace{0.2cm} \\
	Recall of a chunk retrieval describes which proportion of the
	desired lines were retrieved.
	\item $\mbox{F$_{1}$-score} = 2 \cdot \dfrac{\mathit{Precision}
	\cdot \mathit{Recall}}{\mathit{Precision} + \mathit{Recall}}$
	\vspace{0.2cm}\\
	In addition, we calculate the F$_{1}$-score, the harmonic mean
	of precision and recall.
We prefer F$_{1}$ to other aggregate
	measures such as accuracy because for a
	``needle-in-the-haystack'' scenario, we do not want to bloat
	our results by correctly not finding lots of irrelevant log
	lines.
	\item Successful retrieval = $\mathit{true}\ \mathit{iff}\
	\mathit{Recall} = 1, \mathit{false\ otherwise}$  \vspace{0.2cm} \\
	We define a successful retrieval as one where all desired
	lines were
	extracted, therefore when recall is one.
\end{itemize}
